Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
changed capitatlization

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
Mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.

>>>>

It is also worth noticing that in both cases the Kappa statistic increases when
adding social data (100\% and 85\% respectively) which represents a more robust
measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance, and we may also notice that the
mean absolute error decreases, giving stronger confidence to our claims when
considering eventual outcomes.
